Moral Foundations of U.S. Political News Organizations

### 2019-03-24 pilot_manuscript.Rmd
first try at valence for sorces' articles
will do more later

overall valence for each source

>>>>

```{r exp1 source descriptives, results = 'asis', echo = FALSE}
#Get the final dataset split into the 4 sources
final$Source = as.factor(final$Source)
NYtimesDesc1 = subset(final, Source == "NY Times") #number of obs. = number of articles for that source; NYT = 406
NPRDesc1 = subset(final, Source == "NPR") #NPR = 695 articles
FoxDesc1 = subset(final, Source == "Fox News") #Fox = 503 articles
BreitbartDesc1 = subset(final, Source == "Breitbart") #Breitbart = 1,437 articles

##Add valence
#NY Times
NYTimes_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)

for (i in 1:nrow(NYtimesDesc1)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(NYtimesDesc1$stemmed[i], " "))))

#only pull the words in the dataset for each foundation
#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]

#add to the dataset
temp2$URL = NYtimesDesc1$Url[i]
temp2$Source = NYtimesDesc1$Source[i]
temp2$wordcount = NYtimesDesc1$wordcount[i]
temp2$Text = NYtimesDesc1$Text[i]

#bind with original
NYTimes_final_desc = rbind(NYTimes_final_desc, temp2)
}

NYTimes_final_desc$valence = vlookup(NYTimes_final_desc$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#NPR
NPR_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)

for (i in 1:nrow(NPRDesc1)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(NPRDesc1$stemmed[i], " "))))

#only pull the words in the dataset for each foundation
#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]

#add to the dataset
temp2$URL = NPRDesc1$Url[i]
temp2$Source = NPRDesc1$Source[i]
temp2$wordcount = NPRDesc1$wordcount[i]
temp2$Text = NPRDesc1$Text[i]

#bind with original
NPR_final_desc = rbind(NPR_final_desc, temp2)
}

NPR_final_desc$valence = vlookup(NPR_final_desc$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#Fox News
Fox_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)

for (i in 1:nrow(FoxDesc1)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(FoxDesc1$stemmed[i], " "))))

#only pull the words in the dataset for each foundation
#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]

#add to the dataset
temp2$URL = FoxDesc1$Url[i]
temp2$Source = FoxDesc1$Source[i]
temp2$wordcount = FoxDesc1$wordcount[i]
temp2$Text = FoxDesc1$Text[i]

#bind with original
Fox_final_desc = rbind(Fox_final_desc, temp2)
}

Fox_final_desc$valence = vlookup(Fox_final_desc$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

#Breitbart
Breitbart_final_desc = data.frame("URL" = NA, "Source" = NA, "Var1" = NA, "Freq" = NA, "wordcount" = NA, "Text" = NA)

for (i in 1:nrow(BreitbartDesc1)) {
##first make a table of a response, unlisting everything
temp = as.data.frame(table(unlist(strsplit(BreitbartDesc1$stemmed[i], " "))))

#only pull the words in the dataset for each foundation
#temp2 = temp[temp$Var1 %in% unique(ingroup_all$words[ingroup_all$words != "" & ingroup_all$words != "NA" & #!is.na(ingroup_all$words)]), ]

#add to the dataset
temp2$URL = BreitbartDesc1$Url[i]
temp2$Source = BreitbartDesc1$Source[i]
temp2$wordcount = BreitbartDesc1$wordcount[i]
temp2$Text = BreitbartDesc1$Text[i]

#bind with original
Breitbart_final_desc = rbind(Breitbart_final_desc, temp2)
}

Breitbart_final_desc$valence = vlookup(Breitbart_final_desc$Var1, #index in original data
                                  warriner, #where's the stuff you want to put in
                                  "V.Mean.Sum", #what column is the stuff you want
                                  "Word2") #what's the matching index

##Eliminate NAs
NYTimes_final_desc = na.omit(NYTimes_final_desc)
NPR_final_desc = na.omit(NPR_final_desc)
Fox_final_desc = na.omit(Fox_final_desc)
Breitbart_final_desc = na.omit(Breitbart_final_desc)

#Calculate mean valence by source
NYTimes_valence_mean = mean(NYTimes_final_desc$valence)
NPR_valence_mean = mean(NPR_final_desc$valence)
Fox_valence_mean = mean(Fox_final_desc$valence)
Breitbart_valence_mean = mean(Breitbart_final_desc$valence)

```
overall valence for each source
